Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
Dispersal Kernel Grids

```{r}
joint_weib %>%
  group_by(model) %>%
  #sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_shape

@@

```{r fig.width=9, fig.height=3.5}
library(kde1d)

@@

cp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, 1250), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, 1250), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") -> pp.dens

ggplot() +
  np_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = "black", size = 1) +
  lims(x = c(0, 1250), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") -> np.dens

plot_grid(cp.dens, pp.dens, np.dens, nrow = 3)

@@

```{r}
cp.dens +
  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> cp.tail

@@

```{r}
cp.dens +
  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> pp.tail

np.dens +
  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> np.tail

plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
```

>>>>

```{r eval = FALSE}
joint_weib %>%
  group_by(model) %>%
  #sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_shape

@@

```{r fig.width=9, fig.height=3.5, include = FALSE}
library(kde1d)

@@

xmax <- 1500
ncurves <- 50

cp_lines <- purrr::map(seq(1:ncurves), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))

pp_lines <- purrr::map(seq(1:ncurves), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = fig.5col[2]))

np_lines <- purrr::map(seq(1:ncurves), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = fig.5col[3]))

@@

```{r KernelCurves}

coords <- c(600, 0.006)

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> pp.dens

ggplot() +
  np_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  theme(panel.grid.major = element_blank()) +
  NULL -> np.dens

kernelcurvesfig <- plot_grid(cp.dens, pp.dens, np.dens, nrow = 3)
#kernelcurvesfig

```{r eval = FALSE}
cp.dens +
  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> cp.tail

@@

```{r KernelTails}

backgroundcol <- "#f7f2e4"
  #"#f7edd5"

cp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        axis.title.y = element_blank()) -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        axis.title.y = element_blank()) -> pp.tail

np.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        axis.title.y = element_blank()) -> np.tail

kernel_tails_fig <- plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
#kernel_tails_fig
```

```{r KernelGrid}
plot_grid(kernelcurvesfig, kernel_tails_fig, ncol = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)
```
